Towards Bringing Together Numerical Methods for Partial Differential Equation and Image Processing

### 2020-03-29 paper/eccv2020submission.tex
Adding some cptions

@@

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_constant_x}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_constant_y}

  \end{subfigure}
  \begin{center}
    Constant model
  \end{center}

@@

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_speed_x_2}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_speed_y_2}
  \end{subfigure}

  \begin{center}
    Images form the inflow speed model. The upper two are from simulation with $g=1.3$ and the lower ones form simulation with $g=0.1$
  \end{center}

  \begin{subfigure}{.5\textwidth}
    \centering
    % \caption{Fluid model, x-velocity fields}
      \includegraphics[width=1\linewidth]{imgs/single_fluid_x_1}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    % \caption{Fluid model, y-velocity fields}
    \includegraphics[width=1\linewidth]{imgs/single_fluid_y_1}
  \end{subfigure}

  \begin{subfigure}{.5\textwidth}
    \centering
    % \caption{Fluid model, x-velocity fields}
    \includegraphics[width=1\linewidth]{imgs/single_fluid_x_2}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    % \caption{Fluid model, y-velocity fields}
    \includegraphics[width=1\linewidth]{imgs/single_fluid_y_2}
  \end{subfigure}

  \begin{center}
  Images form the viscosity-density model. The upper two are from simulation with $\nu=1.3, \rho=2.3$ and the lower ones form simulation with $\nu=1.3, \rho=2.3$
  \end{center}

@@

\begin{figure}
  \begin{subfigure}{.3\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/single_const_psnr}
  \end{subfigure}
  \begin{subfigure}{.3\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/single_fluid_psnr}
  \end{subfigure}
  \begin{subfigure}{.3\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/single_speed_psnr}
  \end{subfigure}

  \caption{}\label{fig:single_psnr}
\end{figure}

\begin{table}
  \begin{center}
    \begin{tabular}{lcc|cc}

      \textbf{Model type} & \multicolumn{2}{c|}{\textbf{Max difference}}  &  \multicolumn{2}{c}{\textbf{Average difference}}\\
      \hline 
      \multicolumn{3}{c|}{}&&\\
                 & \underline{With pr.} & \underline{without pr.}  &  \underline{With pr}.& \underline{without pr.}\\

      Constant          &  14.6(3.89)&44.0(3.1e+02)&0.599(0.0818)&0.721(0.294)  \\

      Inflow speed      &  32.2(0.297)&45.7(1.47)&0.546(0.00217)&0.929(0.00533) \\

      Viscosity-density &  57.0(1.8e+03)&14.7(7.04)&13.8(1.8e+02)&0.374(0.00824) \\
    \end{tabular}
  \end{center}
  \caption{Your caption.}\label{tab:single}
\end{table}

@@

The viscosity-density and inflow speed models are evaluated with several simulations with different parameters. As it is impractical to give the results of the evaluation of each simulation, here we present only several of them. The showed results, however, are representative of the general performance of our models. For this section, we also limit ourselves only to models that do use the pressure field of the simulations.

@@

\begin{figure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/constant_i10}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/constant_i190}
  \end{subfigure}  
  \caption{}\label{fig:rec_const_psnr}
\end{figure}

\begin{figure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/inflow_i10}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/inflow_i1436}
  \end{subfigure}

  \begin{center}
    Simulation
  \end{center}

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/inflow_39_s0}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/inflow_39_s120}
  \end{subfigure}

  \begin{center}
    Simulation
  \end{center}

  \caption{}\label{fig:rec_speed_psnr}
\end{figure}

\begin{figure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/fluid_25_s0}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/fluid_25_s120}
  \end{subfigure}

  \begin{center}
    Simulation
  \end{center}

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/fluid_100_s0}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/fluid_100_s120}
  \end{subfigure}

  \begin{center}
    Simulation
  \end{center}

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/fluid_300_s0}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/fluid_300_s120}
  \end{subfigure}

  \begin{center}
    Simulation
  \end{center}

  \caption{}\label{fig:rec_fluid_psnr}
\end{figure}

@@

\begin{table}
  \begin{center}
    \begin{tabular}{l|cc|cc}
      \textbf{Frame} & \multicolumn{2}{c|} {\shortstack{\textbf{Simulation 8}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}  &  \multicolumn{2}{c}{\shortstack{\textbf{Simulation 39}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}\\
      \hline 
                     &\multicolumn{2}{c|}{} & &\\
                     & {Average difference} & {Max difference}  &  {Max difference} & {Average difference}\\
      \emph{Frame 1}       &34.27(0.02) & 52.72(0.40)    &35.91(0.02) & 51.76(0.38)   \\
      \emph{Frame 5}       &33.86(0.11) & 60.41(1.62)    &35.84(0.10) & 53.13(0.54)   \\
      \emph{Frame 10}      &33.99(0.17) & 66.04(2.16)    &36.01(0.15) & 54.59(1.14)   \\
      \emph{Frame 15}      &33.80(0.20) & 76.40(3.67)    &35.91(0.20) & 58.90(1.97)   \\
      \emph{Frame 20}      &34.27(0.22) & 75.39(3.07)    &35.89(0.24) & 62.60(2.94)   \\
      \emph{Frame 25}      &33.91(0.22) & 83.45(3.06)    &35.93(0.28) & 61.07(2.60)   \\
      \emph{Frame 30}      &34.13(0.24) & 79.15(2.20)    &35.73(0.33) & 66.69(4.21)   \\
      \emph{Frame 35}      &34.38(0.23) & 83.52(2.09)    &35.94(0.35) & 65.55(4.18)   \\      
    \end{tabular}
  \end{center}
  \caption{Your caption.}\label{tab:recursive_inflow}
\end{table}

@@

% LocalWords:  Convolutional timestep timesteps grayscale cGANs GAN
% LocalWords:  preprocessing postprocessing hyperparameters HiFlow

>>>>

\begin{figure}
  \begin{subfigure}{.3\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/single_const_psnr}
  \end{subfigure}
  \begin{subfigure}{.3\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/single_speed_psnr}
  \end{subfigure}
  \begin{subfigure}{.3\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/single_fluid_psnr}
  \end{subfigure}
  \caption{The evaluation samples for the constant model show how inconsistent its performance can be. We assume this is due to the limited data that the consent model uses. In contrast to that, we see how the viscosity-density model achieves significantly higher average PSNR.\@ On the other hand, the usage of the pressure field decreases the performance of the viscosity-density model. The may be because of the overall complexity of the model. The pressure field only adds another component to it that makes it even more hard to train.}\label{fig:single_psnr}
\end{figure}

\begin{table}
  \begin{center}
    \begin{tabular}{lcc|cc}
      \textbf{Model type} & \multicolumn{2}{c|}{\textbf{Max difference}}  &  \multicolumn{2}{c}{\textbf{Average difference}}\\
      \hline 
      \multicolumn{3}{c|}{}&&\\
                 & \underline{With pr.} & \underline{without pr.}  &  \underline{With pr}.& \underline{without pr.}\\

      Constant           &14.56(1.97)&44.04(18.73)&0.60(0.29)&0.72(0.54)  \\
      Inflow speed       &32.16(0.55)&45.68(1.21)&0.55(0.05)&0.93(0.07)   \\
      Viscosity-density  &57.00(42.46)&14.70(2.65)&13.85(13.43)&0.37(0.09)\\
    \end{tabular}
  \end{center}
  \caption{All of the given numbers are in percent. In the brackets we also give the standard deviation of the corresponding metric. }\label{tab:single}
\end{table}

@@

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_constant_x}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_constant_y}
  \end{subfigure}
  \begin{center}
    Constant model
  \end{center}

@@

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_speed_x_2}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_speed_y_2}
  \end{subfigure}
  \begin{center}
    Images form the inflow speed model. The upper two are from simulation with $g=1.3$ and the lower ones form simulation with $g=0.1$
  \end{center}

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_fluid_x_1}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_fluid_y_1}
  \end{subfigure}

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_fluid_x_2}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_fluid_y_2}
  \end{subfigure}
  \begin{center}
  Images form the viscosity-density model. The upper two are from simulation with $\nu=1.3, \rho=2.3$ and the lower ones form simulation with $\nu=1.3, \rho=2.3$
  \end{center}

@@

@@

The viscosity-density and inflow speed models are evaluated with several simulations with different parameters. As it is impractical to give the results of the evaluation of each simulation, here we present only several of them. The showed results, however, are representative of the general performance of our models. For this section, we also limit ourselves only to models that do use the pressure field of the simulations. All of the given plots show the mean results for each frame across the evaluations of several models that differ only in the used seed during training. We also plot the standard divination across the evaluations.

@@

\begin{figure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/constant_i10}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/constant_i190}
  \end{subfigure}  
  \caption{The simulation that starts at the 10.\@ frame exhibits unintuitive results. This happens because the PSNR is based on MSE and it can go up if the network produces a homogeneous black image. In this case the PSNR can get higher in the second of the predicted frames. This, however, does not meant that the visual fidelity of the frames is good.}\label{fig:rec_const_psnr}
\end{figure}

\begin{figure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/inflow_i10}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/inflow_i1436}
  \end{subfigure}
  \begin{center}
    Recursive evaluations of the inflow speed model on simulation with $g=1.5$. To note is that this simulations was part of the training set. This can explain why the PSNR drops slightly faster on the next charts when it comes to the simulation starting at the 120.\@frame.
  \end{center}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/inflow_39_s0}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/inflow_39_s120}
  \end{subfigure}
  \begin{center}
    Recursive evaluations of the inflow speed model on simulation with $g=3.9358$.
  \end{center}
  \caption{In the evaluations of the inflow speed models, we consistently saw the same behavior as in the constant models. The simulations that at are started at a frame with smaller index are of a lower quality.}\label{fig:rec_speed_psnr}
\end{figure}

\begin{figure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/fluid_25_s0}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/fluid_25_s120}
  \end{subfigure}
  \begin{center}
    Recursive evaluations of the viscosity-density model on simulation with $\rho=4.1764$ and $\nu=0.001023$.
  \end{center}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/fluid_100_s0}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/fluid_100_s120}
  \end{subfigure}
  \begin{center}
    Recursive evaluations of the viscosity-density model on simulation with $\rho=5.7647$ and $\nu=0.001517$.
  \end{center}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/fluid_300_s0}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/charts/fluid_300_s120}
  \end{subfigure}
  \begin{center}
    Recursive evaluations of the viscosity-density model on simulation with $\rho=6.8235$ and $\nu=0.002876$.
  \end{center}  
  \caption{All of the simulations for the charts are from the test set of the viscosity-density model. The evaluations with starting frame of 0 are consistent with the results from the other models. The evaluations starting at frame 120 are, however, much more stable as indicated by the standard deviation. We again attribute that to the over all stability of the model due to the large amount of train data used to train the models of this type.}\label{fig:rec_fluid_psnr}
\end{figure}

@@

\begin{table}
  \begin{center}
    \begin{tabular}{l|cc|cc}
      \textbf{Frame} & \multicolumn{2}{c|} {\shortstack{\textbf{Simulation 8}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}  &  \multicolumn{2}{c}{\shortstack{\textbf{Simulation 39}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}\\
      \hline 
                     &\multicolumn{2}{c|}{} & &\\
                     & {Average difference} & {Max difference}  &  {Max difference} & {Average difference}\\
      \emph{Frame 1}       &34.27(0.02) & 52.72(0.40)    &35.91(0.02) & 51.76(0.38)   \\
      \emph{Frame 5}       &33.86(0.11) & 60.41(1.62)    &35.84(0.10) & 53.13(0.54)   \\
      \emph{Frame 10}      &33.99(0.17) & 66.04(2.16)    &36.01(0.15) & 54.59(1.14)   \\
      \emph{Frame 15}      &33.80(0.20) & 76.40(3.67)    &35.91(0.20) & 58.90(1.97)   \\
      \emph{Frame 20}      &34.27(0.22) & 75.39(3.07)    &35.89(0.24) & 62.60(2.94)   \\
      \emph{Frame 25}      &33.91(0.22) & 83.45(3.06)    &35.93(0.28) & 61.07(2.60)   \\
      \emph{Frame 30}      &34.13(0.24) & 79.15(2.20)    &35.73(0.33) & 66.69(4.21)   \\
      \emph{Frame 35}      &34.38(0.23) & 83.52(2.09)    &35.94(0.35) & 65.55(4.18)   \\      
    \end{tabular}
  \end{center}
  \caption{}\label{tab:recursive_inflow}
\end{table}

@@

% LocalWords:  Convolutional timestep timesteps grayscale cGANs GAN
% LocalWords:  preprocessing postprocessing hyperparameters HiFlow
% LocalWords:  unintuitive
